Formulating and Validating RDF Constraints Generically

### 2015-04-08 paper/paper 2/paper 2.tex
evaluation

\section{Introduction}

%The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
%OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
%Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web. 
%On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
%For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Half-Klingon & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
class & $\neg$E & - & - & E & $\neg$ & - \\
class & E & - & - & A, B & $\sqcap$ & - \\
class & $\neg$F & - & - & F & $\neg$ & - \\
class & F & - & - & C, D & $\sqcap$ & - \\
class & A & - & - & A1, A2 & $\sqcap$ & - \\
property & A1 & isbn & - & string & $\geq$ & 1 \\
property & A2 & isbn & - & string & $\leq$ & 1 \\
class & B & - & - & B1, B2 & $\sqcap$ & - \\
property & B1 & title & - & string & $\geq$ & 1 \\
property & B2 & title & - & string & $\leq$ & 1 \\
class & C & - & - & C1, C2 & $\sqcap$ & - \\
property & C1 & issn & - & string & $\geq$ & 1 \\
property & C2 & issn & - & string & $\leq$ & 1 \\
class & D & - & - & D1, D2 & $\sqcap$ & - \\
property & D1 & title & - & string & $\geq$ & 1 \\
property & D2 & title & - & string & $\leq$ & 1 \\
		\end{tabular}
	\caption{Complex Constraints}
	\label{tab:complex-constraints}
\end{table}

>>>>

\section{Introduction}
\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
%The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
%OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
%Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web. 
%On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
%For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
class & $\neg$E & - & - & E & $\neg$ & - \\
class & E & - & - & A, B & $\sqcap$ & - \\
class & $\neg$F & - & - & F & $\neg$ & - \\
class & F & - & - & C, D & $\sqcap$ & - \\
class & A & - & - & A1, A2 & $\sqcap$ & - \\
property & A1 & isbn & - & string & $\geq$ & 1 \\
property & A2 & isbn & - & string & $\leq$ & 1 \\
class & B & - & - & B1, B2 & $\sqcap$ & - \\
property & B1 & title & - & string & $\geq$ & 1 \\
property & B2 & title & - & string & $\leq$ & 1 \\
class & C & - & - & C1, C2 & $\sqcap$ & - \\
property & C1 & issn & - & string & $\geq$ & 1 \\
property & C2 & issn & - & string & $\leq$ & 1 \\
class & D & - & - & D1, D2 & $\sqcap$ & - \\
property & D1 & title & - & string & $\geq$ & 1 \\
property & D2 & title & - & string & $\leq$ & 1 \\
		\end{tabular}
	\caption{Complex Constraints}
	\label{tab:complex-constraints}
\end{table}
